---
title: "Combine Plot and Table in R"
author: "Scott Stewart"
date: "3/3/2022"
output: 
  rmdformats::readthedown:
    code_folding: show
---

```{r setup-knitr, include = FALSE}
knitr::opts_chunk$set(message = FALSE) # suppress messages
```

## Plot

load packages:
```{r}
library(tidyverse)
library(ggpmisc)
```

### data for plot
```{r}
data <- tibble(
  group = c("A", "A", "A", "A", "B", "B", "B", "B", "C", "C", "C", "C"),
  x = c(1, 5, 15, 20, 3, 11, 15, 18, 6, 10, 17, 16),
  y = c(15, 13, 8, 4, 12, 10, 13, 7, 5, 9, 12, 11))
data
```

### basic plot
```{r}
p1 <- data %>% 
  ggplot(aes(x = x, y = y, fill = group, shape = group)) +
  geom_point(aes(color = group), size = 3)
p1
```

### add options to plot
```{r}
p2 <- p1 + 
  geom_smooth(aes(color = group), 
              method = lm, se = TRUE) + # add lines & confidence bands
  scale_fill_brewer(palette = "Set1") + # colors for confidence bands
  scale_colour_brewer(palette = "Set1") + # colors for lines
  geom_text(x = 15, y = 20, label = "p = 0.05", color = "purple") + # add text
  theme_classic() + # remove gray background
  labs(
    title = "plot title",
    x = "independent variable",
    y = "dependent variable"
  )
p2
```

## Table

### data for table
```{r}
table <- tibble(group = c("A", "B", "C"),
                at_risk = c(10, 13, 18),
                n = c(80, 70, 65))
table
```

### create object from table
```{r}
library(gridExtra)
p3 <- tableGrob(table, rows = NULL, theme = ttheme_gtminimal())
```

## Combine Plot and Table

`draw_plot(obj, a, b, c, d)` will define the starting point, width and height
for each object:  
  
  - `obj` = name of object
  - `a` = relative position of left edge (0 = far left)
  - `b` = relative position of bottom edge (0 = bottom)
  - `c` = relative width (max = 1)
  - `d` = relative height (max = 1)
  
```{r}
library(cowplot)
p4 <- ggdraw() +
  draw_plot(p2, 0, 0.2, 1, 0.8) + 
  draw_plot(p3, 0.1, 0.05, 0.3, 0.15)
p4
```

## Save as Image
```{r message = TRUE}
ggsave("C:/Users/stewartscott/Documents/Programming/R/plot_plus_table.png", p4)
```